---
title: "Untitled"
output: github_document
date: "2023-06-23"
---


# Required packages  

 1 library(httr): used for Working with URLs and HTTP
 2 library(jsonlite):  used for working with JSON data
 3 library(dplyr): used for data manipulation and summarization
 4 library(tidyr):  tidying and reshaping data
 5 library(ggplot2):data visualization and creating plots



# Write function(s) to contact API and return well-formatted data frame

```{r func1}
library(httr)
library(jsonlite)
library(dplyr)

# Function to retrieve recipe data from Spoonacular API
getRecipesByNutrients <- function(apiKey, maxCalories, maxCarbs, maxFatt,maxAlcohol,maxCaffeine,maxCalcium) {
  # API base URL
  base_url <- "https://api.spoonacular.com/recipes/findByNutrients"
  
  # Convert the nutrient values to lowercase and map them to the corresponding abbreviations
  nutrients <- c("calories" = "maxCalories", "carbs" = "maxCarbs", "fat" = "maxFat", "protein" = "maxProtein","alcohol" = "maxAlcohol", "caffeine" = "maxCaffeine","calcium"="maxCalcium")
  nutrientParams <- lapply(nutrients, function(x) {
    if (tolower(x) %in% c("calories", "carbs", "fat", "alcohol", "caffeine","calcium")) {
      x <- nutrients[tolower(x)]
    }
    return(x)
  })
  
  # Set query parameters
  params <- list(
    apiKey = apiKey,
    number = number,
    maxCalories = maxCalories,
    maxAlcohol = maxAlcohol,
    maxCarbs = maxCarbs,
    maxCaffeine = maxCaffeine,
    maxFat = maxFat,
    maxCalcium = maxCalcium,
    )
  
  # Construct API request URL
  url <- paste0(base_url, "/", endpoint)
  
  # Make GET request to the API
  response <- GET(url, query = params)
  
  # Check if the request was successful
  if (http_status(response)$category == "Success") {
    # Parse the response content
    recipeData <- content(response, as = "text")
    parsedData <- fromJSON(recipeData, flatten = TRUE)
    
    # Create a data frame from the parsed data
    df <- as.data.frame(parsedData)
    return(df)
  } else {
    stop("Error: API request failed.")
  }
}

```


# Basic exploratory data analysis  


```{r dataana1}
library(httr)
library(jsonlite)
library(ggplot2)
library(dplyr)
library(tidyr)


# Function to perform exploratory data analysis (EDA)

  recipeData <- getRecipesByNutrients(apiKey= "6b092ffb43d4498c8999b635f46106a3", maxCalories, maxCarbs)
  
  # Create one new variable that is a function of the variables from a data set
  recipeData$caloriesPerCarb <- recipeData$calories / recipeData$carbs
  
  # Create contingency table
  contingencyTable <- table(recipeData$cuisine, recipeData$vegetarian)
  
  # create numerical summaries for some quantitative variables：calories and protein 
   
  summaryByCuisine <- recipeData %>%
    group_by(cuisine) %>%
    summarise(meanCalories = mean(calories), meanProtein = mean(protein))
  
  # Create at least five plots utilizing coloring
  # Bar plot: 
  barPlot <- ggplot(recipeData, aes(x = cuisine, fill = vegetarian)) +
    geom_bar() +
    labs(x = "Cuisine", y = "Count", title = "Recipe Count by Cuisine") +
    theme(legend.title = element_blank())
  barPlot
  
  # Histogram
  histogram <- ggplot(recipeData, aes(x = calories)) +
    geom_histogram(binwidth = 100, fill = "green") +
    labs(x = "Calories", y = "Frequency", title = "Calorie Distribution")
  histogram
  
  # Box plot
  boxPlot <- ggplot(recipeData, aes(x = cuisine, y = protein, fill = vegetarian)) +
    geom_boxplot() +
    labs(x = "Cuisine", y = "Protein", title = "Protein Content by Cuisine") +
    theme(legend.title = element_blank())
  boxPlot
  
  # Scatter plot: Calories per Carb
  scatterPlot <- ggplot(recipeData, aes(x = carbs, y = calories, color = vegetarian)) +
    geom_point() +
    labs(x = "Carbs", y = "Calories", title = "Calories per Carb") +
    theme(legend.title = element_blank())
  scatterPlot
  
 
```





